### 2009-07-30 docs/runtime_parameters/runtime_parameters.tex
removed p0_update_type=1 code
to be consistent with our naming convention, made temp_diffusion_formulation an integer instead of a logical
updated with rp.py

@@

@@

@@

\verb=  p0_update_type  = &   How we update the base state pressure and compute psi. \newline 1 = call {\tt advect\_base\_pres}; \newline 2 = call {\tt enforce\_HSE}.  &  2 \\

@@

\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term.  \newline .true. = in terms of $T$; \newline .false. = in terms of $\rho,p_0,X$.  &  .false. \\

>>>>

\verb=  burner_threshold_cutoff  = &   Mass fraction cutoff for burner\_threshold\_species  used in burner threshold  &  1.e-10 \\
\verb=  burner_threshold_species  = &   Name of the species to be used in burner threshold  &  "" \\

@@

\verb=  do_smallscale  = &   force $\rho_0 = (\rho h)_0 = 0$, {\tt evolve\_base\_state = F} and {\tt beta\_type} = 3  &  .false. \\

@@

\verb=  max_grid_size_base  = &   The largest grid size that will be created using make\_new\_grids for the coarsest level.  Defaults to {\tt max\_grid\_size}.  &  -1 \\

@@

@@

\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term.  \newline 1 = in terms of $T$; \newline 2 = in terms of $\rho,p_0,X$.  &  2 \\
